Continuous Reinforcement Learning

### 2018-06-12 magnitudes.tex
[ADD] Magnitudes.tex

\section{Intuitions}
\label{sec:intuitions}

>>>>

\section{Intuitions}
\label{sec:intuitions}
Reinforcement learning aims at tackling a wide variety of real world problems.
Among them obviously stand physical problems, where an agent interacts with a
physical environment, e.g.\ the real world.

Resistance to a change of time discretization is a desirable property for
algorithms aiming at attacking the reinforcement learning field in physical
setups: such algorithms should only improve as the time discretization is
refined, as refining the time discretization can only increase the amount of 
eploitable information.
